% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref,amsmath}
\usepackage{geometry,textcomp}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Acadia Larsen}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={7in, 9.in},
  left=.75in,
  top=1in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
%	{\huge \name}

% Alternatively, print name centered and bold:
\centerline{\huge \bf \name}

\vspace{0.25in}
\begin{center} 1 Shield Avenue Davis, CA  | 925.818.7179 | \href{mailto:acadia.larsen@gmail.com}{\tt acadia.larsen@gmail.com} \end{center}
%\begin{minipage}{0.5\linewidth}
%  Whittier College \\
%  Student Box 8356 \\
%  13406 E. Philadelphia St.\\
%Whittier, CA 90608 
%\end{minipage}
%\begin{minipage}{0.45\linewidth}
%  \begin{tabular}{ll}
%    Phone: & (925) 818-7179 \\
%    Email: & \href{mailto:alarsen@poets.whittier.edu}{\tt alarsen@poets.whittier.edu} \\
%%    Homepage: & \href{} \\
%  Major: &  Mathematics\\
%Minor: &  Economics \\
%  GPA: & 3.72
%  \end{tabular}
%\end{minipage}


%\section*{Personal}

%\begin{itemize}
%\item Born on September 29, 1895.
%\item United States Citizen.
%\end{itemize}
%\begin{center}{\bf Objective}:  Seeking Employment as a mathematics educator in New York Public Schools. \end{center}
\vspace{0.1in}

\section*{{\bf Education}}
\textbf{Ph.D in Applied Mathematics}, University of California, Davis, 2020- 2025 (Expected).\\ 
\textbf{M.Sc. in Mathematics}, The University of Texas Rio Grande Valley, December 2018. \\ Dean's Graduate Research Assistant\\ Thesis: \textit{Partition Identities for Partitions with Parts from a Finite Set}. \vspace{.2cm}\\
%Non-degree student, Colorado University: Denver, Graduate Department of Mathematics, Fall 2016 - Spring 2017.\\
\textbf{B.A. in Mathematics}, Minor in Economics, Whittier College, {\it cum laude}, May 2014. \vspace{.2cm}\\
%\indent {\small {\bf- Awards}: Dean's list, Spring 2011 - Spring 2012, Pyle Prize for outstanding graduate in mathematics, Pi Mu Epsilon (Math Honor Society), Omicron Delta Epsilon (Economics Honor Society). }\\
Budapest Semesters Abroad in Mathematics, Spring 2013. \\

\vspace{-.1in} 
%\section*{{\bf Skills}}
%-Fluent in Python scripting language, C++ programing language, and LaTeX markup language.\\
%{\small During my research programs I developed programs to implement mathematical tools to help solve research questions.}
%\\-Intentional collaboration to implement innovative ideas in a variety of settings.
%\\-Small group teaching and tutoring experience for individualized instruction.
%\\-Computer repair, virus removal, hardware replacement and network printing.
%\\{\small Quickly and effectively diagnose hardware and software issues on laptops and preform repair.}
%\\-Data entry and cash register experience.

% \section*{{\bf Coursework}}
% \begin{minipage}{0.5\linewidth}
%  Calculus \& Analytical Geometry II, III \\
%     Probability and Statistics \\
% Numerical Analysis\\
% Introduction to Analysis I \& II\\
% Complex Functions*\\
% Introduction Linear Algebra and Differential Equations \\
% Set Theory*\\
% Applied Combinatorics**\\
% Introduction to Programing I \& II\\
% \end{minipage}
% \begin{minipage}{0.45\linewidth}
% Discrete Mathematics \\
%  Abstract Thinking (intro to proofs course)\\
%  Modern Algebra I\\
% %Galois Theory*\\ 
% Independent Study: Integer Partitions\\
% %Combinatorics I*\\
% History of Mathematics\\
% Introduction to Number Theory*\\
% Linear Algebra\\
% Linear Programing**\\
% Senior Seminar (Senior Thesis)\\
% \end{minipage}
%Relevant Employment History
\section*{{\bf Full Employment History}}
{\bf University of Texas: Rio Grande Valley} Part-Time Lecturer, August 2019- August 2020 \\ %{\small Lecturer delivering quality traditional and computer assisted courses. I have taught College Algebra, Elementary Statistics, and Calculus 1.  }\vspace{.2cm}\\
{\bf Course Hero,} Item Writer (contract), June 2019 - March 2020 \\ 
{\small I author high quality supplemental textbook resources for popular collegiate mathematics textbooks in a collaborative environment. Additional duties include scripting explanatory graphs in JSX graph environment, accurately recording key notations in the text, and providing clear and concise explanations that help students succeed.  } \vspace{.2cm}\\
{\bf The University of Texas: Rio Grande Valley,} Graduate Assistant, September 2017 - December 2018.\\
{\small My duties were to assist Dr. Kronholm in research projects, grade papers from an introduction to proofs class, and serve as a Graduate Teaching Assistant teaching one section of College Algebra with 39 students.} 
%{\small \textbf{Supervisor:} Dr. Timothy Huber, \textbf{Salary:} \$15,000 year for Deals Fellowship, \$12,000 Standard Graduate Assistant Duties, 20 hours per week.}
% {\small Research assistant to Dr. Kronholm studying restrictions on integer partitions. We study the combinatorial and number theoretic properties of integer partitions by using techniques from the theory of generating functions, polyhedral geometry, and group theory. Furthermore, we find applications of partitions to computing sizes combinatiorial optimization problems.}
\vspace{.2cm}\\
{\bf Exl Learning,} Tutor and Summer Camp Instructor, February 2017- August 2017.\\
{\small I effectively tutored $5^{th}$ to $12^{th}$ grade students in core mathematics skills, algebra, grade level material, college admission test perpetration, and calculus  for Denver's premiere tutoring center. My students expended growth and increased test scores in every instance.  Additionally, I lead a variety of summer camps in which $3^{rd}$ though $8^{th}$ graders learned about puzzles, engineering, and fiction. Parents reported that their students gave high praise for the instruction and activities in these summer camps.  }
\vspace{.2cm}\\
{\bf Royal Crest Dairy}, Route Driver, August 2016 - December 2016. \\
%{\indent {\bf \small Delivered fresh milk products to 150+ homes per night in a timely and safe manner.}}\\
{\small I delivered fresh milk products to 150+ homes in the greater Denver Metro area meeting delivery deadlines and ensuring customer satisfaction.  During the month of November, I was awarded Driver of the Month for high customer satisfaction and accurate deliveries. }\vspace{.2cm}\\
{\bf Denver Math Fellow (Americorps),} Lead Fellow, August 2014 - August 2016. \\
%{\indent{ \bf \small Americorps year of service resulting improved student and community relationships.}}\\
{\small I effectively tutored, taught, and mentored small groups (1 - 5 students) of $9^{th}$ grade students in math for Algebra 1, Geometry, Algebra 2, and foundational topics at Denver Center for International Studies at Montbello, an under served school in Denver Public Schools school district. Furthermore, I worked in a team environment to develop individualized objective oriented lesson plans for small group instruction. After my first year, I became a Lead Fellow which provided an approximate 10\% salary increase and am supported by an Americorps grant.} \vspace{.2cm}\\
% {\bf Mellon Mays Fellowship}, Research Fellow, May 2012-May 2014. 
% %\\{\indent{ \bf \small Research fellowship resulting in a published academic paper.}}
% \\{\small I studied restriction of integer partitions with Dr. Brandt Kronholm. I developed computational tools and algorithms in Python to quickly and effectively enumerate some restricted integer partitions for larger primes. With this knowledge, I, with Dr. Kronholm, conjectured and proved several statements about the arithmetic properties of some restricted integer partitions. This work lead to a published academic paper in the Annals of Combinatorics.} \vspace{.2cm}\\
{\bf Whittier College Math Department}, Grader, September 2010-December 2011, September 2012-December 2012, September 2013-May 2014. 
%\\{\indent{ \bf \small Graded the highest level courses allowed for undergraduate students.}}
\\{\small A work study position where I quickly and accurately graded homework for courses including Calculus and Analytic Geometry I \& III, College Mathematics, and Introduction to Linear Algebra and Differential Equations.}\vspace{.2cm}\\
%\textbf{For a full employment history of the past 10 years, please email me. }
%{\bf Private Mathematics Tutor}, November 2013- May 2014. \\{\small Tutored $7^{th}-9^{th}$ grade students in Mathematics. All students experienced significant improvement in understanding of material, including a failing grade to an A.}\vspace{.2cm}\\
{\bf Whittier College Information Technology Services},  Student Computer Technician,
	 September 2010-December 2012, September 2013-May 2014. \\
%	 {\indent{ \bf \small Moved to the highest work study pay grade after one semester.}}\\
{\small Successfully repaired hardware and software issues with student and faculty laptop and desktop computers in both Windows and Mac environments. Additionally, I performed accurate installation and repair of network printers for various facilities around campus. Additional duties included courteously answering faculty and student questions as well as professional delivery of classroom technology. }\vspace{.2cm} \\
%  {\bf Oregon State University: Research Experience for Undergraduates}, Research Fellow, June 2013-August 2013. 
%  \\%{\indent{ \bf \small Research fellowship resulting in a published academic paper.}}\\
% {\small I studied overpartitions with Dr. Holly Swisher. I made key advances on previously unsolved research question as well as pioneered techniques which lead to the solution of our research question. This work lead to an academic paper published in the International Journal of Number Theory. }\vspace{.2cm} \\
% %Please contact \href{mailto:acadia\_larsen@dpsk12.org}{\tt acadia\_larsen@dpsk12.org} for references. 
% {\bf California State University: Channel Islands Research Experience for Undergraduates}, Research Fellow, June 2012 - August 2012. 
% \\ {\small  Research Fellow studying Young tableaux with Dr. Heather Russel. With Dr. Russel and other students, I created a program to quickly diagram $SL_n$ webs creating a valuable tool in our research. Additionally, we made progress in finding an irreducible basis for $SL_4$ webs.}\vspace{.2cm}\\
{\bf Target Pleasant Hill}, Remodel Team Member,
	 June 2011- August 2011.  
\\{\small As a temporary remodel employee, I  accurately set up new shelving and store plans in a team environment. Furthermore, I assisted customers find items in the store are well as preformed cash register duties when needed.}


%\section*{Research}
%\subsection*{Restricted Integer Partitions Sum  Congruences} 
%Summer 2012- Present,  \begin{it}Mellon Mays project\end{it}, Mentor: Dr. Brandt Kronholm
%\\Abstract: The restricted partitions of a number $n$ into exactly $m$ parts, denoted $p(n,m)$ is relatively unexplored. Restricted partitions are periodic modulo $m$. It can be observed that  $p(55+r,5) + p(55-r,5) \equiv p(r)  \pmod 5$ for $r \in \{0,1,2, ... 9\}$. It begs the questions of when  two restricted partitions of $m$ are added together and taken modulo $m$ congruent to $p(n)$ (the partition numbers).  By using modern computational tools, investigation quickly shows that similar statements are true for an odd primes, particularly for values near the ends of their respective periods. We attempt to show when statements like the above are true and when they occur. 
%\subsection*{The Jeu-de-Taquin operation on Young tableaux and the relation to $sl_4$ webs}
%Summer 2012 - \begin{it}Cal State Channel Islands REU\end{it}, Mentor: Dr. Heather Russell
%\\Abstract: Webs are trivalent, planar graphs equipped with certain reduction rules that come from representation theory of special linear algebras. For $r\geq 2$, work of Westbury and Fontaine establishes a bijection between rectangular standard Young tableaux with $r$ rows and $sl_r$ basis webs. The jeu-de-taquin operation is a combinatorial process on standard Young tableaux.  In the $sl_2$ and $sl_3$ case, Westbuy's basis web associated with performing jeu-de-taquin on a standard Young tableau is a rotation of the web associated with the original tableau. However, we show by counterexample that the $sl_4$ webs developed by Westbury's algorithm do not obey this principle. We propose an alternate method for building basis webs that will satisfy this rotational property and show that this indeed yields a basis in the $(2,2,2,2)$ case. This new basis could simplify the study of symmetric group actions on basis webs as well as the construction of an algorithm from semistandard tableaux to webs with different boundary. 

%\section*{Programs written}
%\subsection*{Web -> LaTeX}
%Developed at Cal State Channel Islands REU - version 1.0
%\\Generates LaTeX code for Young Tableaux, m-diagrams, webs from m-diagrams, Westbury diagrams (and related materials), delta diagrams, webs from delta diagrams. 
%\\Avaliable for download at (put link here)
\section*{\textbf{Grants and Awards}}
\textbf{Japan Society for Promotion of Science }, (2018), a \textyen 538000 (~\$5300) award to conduct research on algorithms and voting games in Japan.  \vspace{.2cm}\\
\textbf{SMART Award}, (2018), a \$2000 award for the semester to lead three undergraduate students in mathematical research via the Student Mentoring and Research Training program at UTRGV.  \vspace{.2cm}\\
\textbf{Dean's Graduate Research Assistant at UTRGV}, (2017-2018), a \$15000 research stipend and 2 years of tuition wavers at UTRGV.  \vspace{.2cm}\\
\textbf{Pyle Prize for outstanding graduate in mathematics}, (2014), an award recognizing one outstanding graduate in mathematics at Whittier College. \vspace{.2cm}\\
\textbf{Mellon Mays Undergraduate Fellowship}, (2012-2014) A \$10,000 award to conduct research as an underrepresented undergraduate. 

\section*{\textbf{Research Interest and Experience}}
I am interested in enumerative combinatorics, partition theory, number theory, combinatorial optimization, applications of computer aided proofs, algorithm design, and education.\vspace{.2cm} \\ %development in number theory, and applications of computer aided proofs to combinatorics and number theory.  \vspace{.2cm}\\ 
 {\bf Oregon State University: Research Experience for Undergraduates}, June 2013-August 2013.\\
{\small I studied overpartitions with Dr. Holly Swisher. I made key advances on a conjecture of Mao regarding inequalities of rank and crank moments of overpartitions.  %previously unsolved research question as well as pioneered techniques which lead to the solution of our research question. 
This work lead to an academic paper published in the International Journal of Number Theory. }\vspace{.2cm} \\
{\bf California State University: Channel Islands Research Experience for Undergraduates}, June 2012 - August 2012. 
\\ {\small  I studied representations of Young tableaux with Dr. Heather Russel. With Dr. Russel and other students, I created a program to quickly diagram $SL_n$ webs creating a valuable tool in our research. Additionally, we made progress in finding an irreducible basis for $SL_4$ webs.}\vspace{.2cm}\\
\section*{Technical Skills}
\textbf{Programming Languages:} I am proficient programming in C++ and Python. I have a rudimentary understanding of SQL. \vspace{.2cm}\\
\textbf{Computer Algebra Systems/Specialty Packages:} I am experienced in AMPLE, Maple, Mathematica, and Sage.\vspace{.2cm}\\ 
\textbf{Algorithm Design:} I have experience designing mathematically sound and efficient algorithm for discrete problems including optimization problems. \vspace{.2cm}\\ 
\textbf{Office Software:} I am proficient in Microsoft Office Suite and LaTeX.
\section*{{\bf Publications}}
%1. \textit{Methods for Proving Cranks of Partitions of $n$ into at Most $m$ parts} with Dennis Eichhorn, Brandt Kronholm, and Dennis Rodriguez. In Preparation.
%\vspace{.2cm}\\
$\bullet$ \textit{Cranks for partitions with bounded largest part}. With Brandt Kronholm and Dennis Eichhorn, Submitted.
$\bullet$ \textit{A Generalization of Partition Identities for First Differences of Partitions of $n$ into at Most $m$ Parts}. Electronic Journal of Combinatorics, July 2021. \vspace{.2cm}\\
$\bullet$ \textit{Quasipolynomials and Maximal Coefficients of Gaussian Polynomials.} with Angelica Castillo, Stephanie Flores, Anabel Hernandez, Brandt Kronholm, and Arturo Martinez. Annals of Combinatorics, November 2019.\vspace{.2cm}\\ 
$\bullet$ \textit{A Survey of Divisibility Proprieties of the Partition Function and Related Functions.}  The Mellon Mays Undergraduate Fellowship Journal, February 2015. \vspace{.2cm}\\
$\bullet$ \textit{Inequalities For Positive Rank and Crank Moments of Overpartitions} with Alexa Rust and Holly Swisher. International Journal of Number Theory, December 2014. \vspace{.2cm}\\
$\bullet$ \textit{Symmetry and Prime Divisibility Properties of the Generating Function for Partitions of $n$ into Exactly $m$ Parts} with Brandt Kronholm. Annals of Combinatorics, March 2014. \\

% On parts of topological graph theory: Conditions of Planarity and Thickness of Graphs. {\it Unpublished Senior Thesis}. January 2014.
\section*{{\bf Conference Presentations}} 
\begin{itemize}
\item \textbf{South Texas Discrete Geometry and Algebraic Combinatorics Conference}, South Padre Island, `' . September 28, 2019. 
\item \textbf{Joint Mathematics Meetings 2018}, Baltimore, `A Generalization of First Difference Identities for Partitions of $n$ Into at Most $m$ Parts' (invited talk) - Special Secession on Partitions, January 16-20 2019. 
\item \textbf{Graduate Student Combinatorics Conference}, University of Texas at Dallas, 'First Difference Identities for Partitions of $n$ Into at Most $m$ Parts' (talk),  April 7, 2018.
%\item February 28, 2018, (Poster). 
\item \textbf{Pacific Coast Undergraduate Mathematics Conference}, Pepperdine University, `Inequalities for Rank and Crank Moments of Overpartitions' (talk), March 8, 2014.
\item \textbf{Joint Mathematics Meetings 2014}, Baltimore, `Inequalities for Rank and Crank Moments of Overpartitions' (poster), January 15-18, 2014.
\item \textbf{Southern California Undergraduate Research Conference}, `Ramanujan-like Restricted Integer Partitions Sums' (talk),  Whittier College, November 23, 2013.
\item \textbf{Mellon Mays Undergraduate Fellowship West Coast Conference}, `Ramanujan-like Restricted Integer Partitions Sums',  University of California: Berkeley, October 31- November 3, 2013.
%\item January 9-12, 2013, Joint Mathematics Meetings 2013, San Diego, California (Attended).
\item \textbf{Southern California Undergraduate Research Conference}, `Ramanujan-like Restricted Integer Partitions Sums' (talk), University of California: Channel Islands, November 17, 2012.
\item \textbf{Ramanujan 125}, University of Florida, Attended, November 5-7, 2012.
\item \textbf{Ivy STEM+ Symposium}, University of Pennsylvania, , `Ramanujan-like Restricted Integer Partitions Sums' (poster), October 4-6, 2012.
%\item March 10, 2012 Pacific Coast Undergraduate Mathematics Conference, California Polytechnic Institute: Pomona, California (Attended).
\end{itemize}

\section*{{\bf Activities}}
{\bf Secret Student Seminar} (University of Texas: Rio Grande Valley), Organizer, Spring 2018.\vspace{.2cm}\\
{\bf Mathematics Club} (Whittier College), Member 2010-Spring 2012, Treasurer, Fall 2012-Spring 2012, President, Fall 2013-Spring 2014. \vspace{.2cm}\\
{\bf Pi Mu Epsilon} Whittier College Chapter, Member Spring 2012-Spring 2013, President Fall 2013-Spring 2014.\vspace{.2cm} \\

%{\bf Rock climbing} - I boulder indoors and have put up a V5 problem.\\
%{\bf Trail running} - I like to run long distances in the mountains. \\
%{\bf Backpacking} - I have done several solo backpacking trips. \\
\section*{{\bf References}}
\subsection*{Dr. Timothy Huber}
Timothy Huber, Associate Professor of Mathematics
\\University of Texas, Rio Grande Valley
\\1201 W University Dr Edinburg, TX 78539
\\Tel: 956.665.3451
\\E-mail: \href{mailto:timothy.huber@utrgv.edu}{\tt timothy.huber@utrgv.edu}


%\subsection*{Ivan Gutierrez}
%Ivan Gutierrez, User Support Manager
%\\Whittier College
%\\13406 E. Philadelphia St. 
%\\Whittier, CA 90608
%\\Tel: 562.907.4287
%\\E-mail:  \href{igutierrez@whittier.edu }{\tt igutierrez@whittier.edu }
\subsection*{Dr. Brandt Kronholm}
Brandt Kronholm, Assistant Professor of Mathematics
\\University of Texas Rio Grande Valley
\\1201 W University Dr, Edinburg, TX 78539
\\Tel: 866.441.8872
\\E-mail:  \href{mailto:brandt.kronholm@utrgv.edu}{\tt brandt.kronholm@utrgv.edu}
\subsection*{Karmen Smith}
Karmen Smith, High School Integrated Math Teacher
\\ Castle View High School
\\ 5254 N. Meadows Dr, Castle Rock, CO 80109
\\Tel: 303.387.9000 (School office)
\\E-mail: \href{karmen.smith@dcsdk12.org}{\tt karmen.smith@dcsdk12.org}
\subsection*{Jamie Spears}
Jamie Spears, Senior Manager 
\\ DSST Public Schools Home Office, 3401 Quebec Street, Suite 2000, Denver, CO 80207
\\Tel: 303.524.6324
\\ E-mail: \href{Jamie.Spears@scienceandtech.org}{\tt Jamie.Spears@scienceandtech.org}
% \subsection*{Dr. Adrian Riskin}
% Adrian Riskin, Professor of Mathematics
% \\Whittier College Math Department
% \\Stauffer Science building Office: Science 105C
% \\Tel: 562.907.4200 ext.4454
% \\E-mail: \href{mailto:ariskin@whittier.edu}{\tt ariskin@whittier.edu}
%\subsection*{Dr. Mark Kozek}
%\subsection*{Dr. Heather Russell} 
% Heather Russell, Assistant Professor of Mathematics
%\\Department of mathematics and Computer Science, Washington College
%\\300 Washington Avenue
%\\Chestertown, Maryland 21620
%\\E-mail:  \href{mailto: hrussell2@washcoll.edu}{\tt hrussell2@washcoll.edu}
% \subsection*{Dr. Holly Swisher}
% Holly Swisher, Associate Professor of Mathematics
% \\Department of Mathematics, Oregon State University
% \\Corvallis, OR, 97331-4605, USA
% \\Tel: 541.737.5167
% \\E-mail: \href{mailto:swisherh@math.oregonstate.edu}{\tt swisherh@math.oregonstate.edu}
%\subsection*{Dr. Mark Kozek}
%\subsection*{Dr. Heather Russell}
% Heather Russell, Assistant Professor (NTT) of Mathematics 
%\\Department of Mathematics
%\\University of Southern California
%\\3620 South Vermont Ave.
%\\KAP 108
%\\Los Angeles, CA 90089-2532
%\\E-mail:  \href{mailto: heathemr@usc.edu}{\tt heathemr@usc.edu}


%\section*{Publications}

%\subsection*{Journal Articles}

%\begin{itemize}
%\item A General Mathematical Theory of Depreciation, 1929, {\it Journal
    %of The American Statistical Association} 20, 340--353.
%\item Differential Equations Subject to Error, 1927, {\it Journal of The
    %American Statistical Association}.
%\item Applications of the Theory of Error to the Interpretation of
  %Trends (with H. Working), 1929, {\it Journal of the American
    %Statistical Association}.
%\end{itemize}

%\subsection*{Proceedings}

%\begin{itemize}
%\item A generalized T-Test and measure of multivariate dispersion,
  %Proc. Second Berkeley Symposium of Mathematical Statistics and
  %Probability, 1951.
%\end{itemize}

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}
